Report on Effect Size Translation

### 2020-11-24 report.Rmd
Clean missing

converted_data %>%
  group_by(std_eff_name, es) %>%
  count(sort = TRUE) %>%
  gt() %>%
  tab_header(
    title = "Coversion of effect sizes",
    subtitle = "New Effect Name - Old Effect Name"
  )
```

>>>>

converted_data %>%
  group_by(std_eff_name, es) %>%
  count(sort = TRUE) %>%
  ungroup() %>%
  set_names(c("New Name", "Old Name", "n")) %>%
  gt() %>%
  tab_header(
    title = "Coversion of effect sizes",
    subtitle = "New Effect Name - Old Effect Name"
  )
```
